Reactor like TGE model

### 2019-04-15 AYSS-2019/presentation/main.tex
minor fix

\usebackgroundtemplate{}
\begin{frame}
\frametitle{Reactor Like TGE model}
\begin{columns}
    \begin{column}{0.5\textwidth}
{\large         As simplification case consider mean global gain:
        \begin{itemize}
            \item  If global gain is $\large 1$ --- exponential rise up breakdown or local micro-breakdown
            \item If global gain is $\le 1$ --- exponential decay to background radiation
        \end{itemize}}
    \end{column}
    \begin{column}{0.5\textwidth}
        \begin{figure}[htb]
            \centering
            \includegraphics[width=1\columnwidth]{aragats.png}
            \\
            \centering{Observation TGE on Aragats mount}
        \end{figure}

>>>>

\usebackgroundtemplate{}
\begin{frame}
\frametitle{Reactor Like TGE model}
\begin{columns}
    \begin{column}{0.5\textwidth}
{\large         As simplification case consider mean global gain:
        \begin{itemize}
            \item  If global gain is $> 1$ --- exponential rise up breakdown or local micro-breakdown
            \item If global gain is $< 1$ --- exponential decay to background radiation
        \end{itemize}}
    \end{column}
    \begin{column}{0.5\textwidth}
        \begin{figure}[htb]
            \centering
            \includegraphics[width=1\columnwidth]{aragats.png}
            \\
            \centering{Observation TGE on Aragats mount}
        \end{figure}
